Care Phenotypes: A Novel Approach to Understanding Healthcare Data Collection Patterns

### 2025-03-29 docs/manuscript/manuscript.tex
V3.

>>>>

\subsection{Core Functionality Implementation}

\subsubsection{Clinical Factor Adjustment}

We implemented a robust system for adjusting care patterns based on clinical factors:
\begin{itemize}
    \item Regression-based adjustment for multiple clinical factors
    \item Handling of missing values and outliers
    \item Preservation of data structure and relationships
    \item Comprehensive logging and error tracking
\end{itemize}

\subsubsection{Pattern Analysis}

Our implementation includes sophisticated methods for analyzing care patterns:
\begin{itemize}
    \item \textbf{Pattern Consistency}: Evaluation of care pattern stability across different measures
    \item \textbf{Unexplained Variation}: Quantification of variations not explained by clinical factors
    \item \textbf{Data Quality}: Comprehensive validation of pattern integrity
\end{itemize}

\subsubsection{Data Preprocessing}

We implemented a comprehensive suite of data preprocessing methods:
\begin{itemize}
    \item \textbf{Missing Value Handling}: Multiple strategies including mean, median, mode, and deletion
    \item \textbf{Outlier Detection}: Z-score based detection with configurable thresholds
    \item \textbf{Data Normalization}: Standardization of measurements for consistent analysis
\end{itemize}

\subsection{Error Handling and Validation}

Our implementation includes robust error handling and validation mechanisms:
\begin{itemize}
    \item \textbf{Input Validation}: Comprehensive checking of data structure and content
    \item \textbf{Type Safety}: Strict type checking and conversion
    \item \textbf{Error Logging}: Detailed logging with context and traceback information
    \item \textbf{Custom Exceptions}: Domain-specific error types for better error handling
\end{itemize}
